Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2020-01-10 paper/paper.Rmd
time taken results

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE, 
  message = FALSE,
  cache = TRUE)
```

@@

Responses from 95 participants were collected. Three participants provided no answers for any task, and their data was removed. Set A was evaluated by 42 participants, and 53 evaluated set B. This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that are analysed on accuracy and speed.

@@

Table \ref{detect_glm1} is a summary of the generalised linear mixed effects model.
The estimate of the intercept represents the detection rate for the Choropleth display of the NW-SE trend.

@@

The model summary in Table \ref{tab:detect_glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
The baseline trend model used is the NW-SE trend, the detection rate is expected to decrease comparatively for choropleth displays of the Three Cities and All Cities trends. However, when the interaction is considered the detection rate is expected to increase for the Three Cities and All Cities trends shows in the Hexagon tile map display.

@@

The amount of time taken for a participants to submit a response is explored. 
The time considered was the amount of time it took for a participant to submit their choice of plot, the reason for their choice, and the perceived difficulty of the choice. The time was taken when each participant hit "Next".

The relationship between time taken to submit, and the correct detection by the participant of the real data display in a lineup is considered in Figure \ref{fig:hist_height}. The bimodal distributions are similar across the type of display and the trend model hidden in the real data plot.
The hexagon map displays have a peak for the group that took up to 5 seconds to submit a response. When viewing a choropleth map display, the second peak occured at around 20 seconds. The longest a participant took to respond was 60 seconds.

@@

```{r beeswarm, fig.cap = "The beeswarm plots show the distribution of the time taken to submit a response for each combination of trend and type of display. The time taken shown by the height of the point for each evaluationq1. The height of the histogram bars show how many evaulations were submitted within each time window. The orange regions of the bars show the amount of correct detections, and the green regions are the amount of incorrect detections."}
# Di playing
s <- d %>% group_by(type, trend, detect) %>%
  summarise(m=median(time_taken), 
            q1=quantile(time_taken, 0.25), 
            q3=quantile(time_taken, 0.75))
library(ggbeeswarm)
ggplot() + 
  geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
  geom_point(data=s, aes(x=type, y=m, colour=type), size=5, alpha=0.7) +
  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
  scale_colour_brewer(palette = "Dark2") +
  facet_grid(trend~detect)
```

The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally. Each point is randomly placed, but regions with more points require points to be placed further from center. For the NW-SE distribution, it is equally likely that quick responders will be correct or incorrect. It is more likely that participants picked the correct response if they took longer to respond. For the Choropelth

@@

The choropleth map displays that included a distribution of Three Cities was very difficult for participants.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE, 
  message = FALSE,
  cache = FALSE)
```

@@

Responses from 95 participants were collected. Three participants provided no answers for any task, and their data was removed. Set A was evaluated by 42 participants, and 53 evaluated set B. This resulted in 1104 evaluations, corresponding to 92 subjects, each evaluating 12 lineups, that are analysed on accuracy and speed. The certainty and reasons of subjects in their answers is also examined.

@@

Table \ref{detect_glm1} is a summary of the generalised linear mixed effects model, testing the effect of plot type and trend model on detection rate. The results support the summary from Figure \@ref{detection_compare}. All terms are statistically significant. Overall, the hexagon tile map performs marginally better than the choropleth for all trend models, which is a pleasant surprise. Detection rate is lower for the Three Cities and All Cities, than the NW-SE group. The hexagon tile map has a substantially higher detection rate than the choropleth for Three Cities and All Cities. XXX Put a number for each of these.

@@

<!-- The model summary in Table \ref{tab:detect_glmer1} shows that the predicted log odds of the detection rate is 0.46 times that of the choropleth lineups, for the lineups of hexagon tile map. 
The baseline trend model used is the NW-SE trend, the detection rate is expected to decrease comparatively for choropleth displays of the Three Cities and All Cities trends. However, when the interaction is considered the detection rate is expected to increase for the Three Cities and All Cities trends shows in the Hexagon tile map display.
-->

@@

Figure \ref{fig:beeswarm} shows the time taken for participants to evaluate each lineup, separately for trend model, whether the data plot was detected or not, and type of plot, as horizontally jittered dot plots.  The time taken to complete an evaluation ranged from milliseconds to 60 seconds. The average time taken for type of display is displayed as a large colored dot on each plot. There is little difference in the average time taken to read a choropleth or hexgon tile map. There is also very little difference in evaluation time whether the data plot was detected or not.

<!-- The amount of time taken for a participants to submit a response is explored. 
The time considered was the amount of time it took for a participant to submit their choice of plot, the reason for their choice, and the perceived difficulty of the choice. The time was taken when each participant hit "Next".

The relationship between time taken to submit, and the correct detection by the participant of the real data display in a lineup is considered in Figure \ref{fig:hist_height}. The bimodal distributions are similar across the type of display and the trend model hidden in the real data plot.
The hexagon map displays have a peak for the group that took up to 5 seconds to submit a response. When viewing a choropleth map display, the second peak occured at around 20 seconds. The longest a participant took to respond was 60 seconds. 
-->

@@

```{r beeswarm, fig.cap = "The distribution of the time taken (seconds) to submit a response for each combination of trend, whether the data plot was detected, and type of display, shown using horizontally jittered dotplots. The coloured point indicates average time taken for each plot type. Although some participants take just a few seconds per evaluation, and some take as much as mcuh as 60 seconds, but there is very little difference in time taken between plot types.", fig.height=8}
# Di playing
s <- d %>% group_by(type, trend, detect) %>%
  summarise(m=median(time_taken), 
            q1=quantile(time_taken, 0.25), 
            q3=quantile(time_taken, 0.75))
library(ggbeeswarm)
ggplot() + 
  geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
  geom_point(data=s, aes(x=type, y=m, colour=type), size=5, alpha=0.7) +
  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
  scale_colour_brewer("", palette = "Dark2") +
  facet_grid(trend~detect) + 
  ylab("Time taken (seconds)") + xlab("") +
  theme(legend.position="bottom")
```

<!-- The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally. Each point is randomly placed, but regions with more points require points to be placed further from center. For the NW-SE distribution, it is equally likely that quick responders will be correct or incorrect. It is more likely that participants picked the correct response if they took longer to respond. For the Choropelth

@@

The choropleth map displays that included a distribution of Three Cities was very difficult for participants. 
-->

### 2020-01-10 paper/paper.tex
time taken results

\hypersetup{
            pdftitle={An Experiment Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
            pdfkeywords={statistics, visual inference, geospatial, population},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{An Experiment Comparing the Effectiveness of the Choropleth Map with a
Hexagon Tile Map for Communicating Cancer Statistics}

@@

Australia is an extreme case of heterogenous geographic units, with
large difference between the smallest and largest geographic units
across various granularities. To communicate information regarding the
small inner-city geographic units of Australian cities an alternative
display must be employed. This will emphasise the value of the statistic
for areas with high population. Figure @ref(fig:liver) shows the
distribution of the smoothed average amount of Liver cancer diagnoses
for Australian Males from 2005-2014. These inner-city areas are not
visible on the choropleth map (a). The hexagon tile map (b) shows orange
hexagons for the inner-city SA2s with higher than average levels of
diagnoses in the capital cities of Melbourne and Sydney. The northern
Queensland, and Northern Territory SA2's with higher than average rates
are still visible but use less map space on the hexagon tile map. There
are still many light blue areas in both displays.

@@

The null model imposed suggests that neighbours are related. The
randomness imposed was smoothed to mirror the practice taken by the
Australian Cancer Atlas. This smoothing allowed neighbours to be related
to each other and show distributions similar to the Liver cancer
distribution shown in @ref(fig:liver).

@@

Replicate 3 of the All Cities distribution is shown in
@ref(fig:compare). The same data set is shown in both displays, the
difference is the land area of each SA3 is coloured in the choropleth
and the hexagon representing the SA3 is coloured in the Hexagon Tile
Map. Many maps in the Choropleth lineup (a) are coloured yellow, two are
half light blue, and two are obviously blue. Only one of the maps looks
red.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/compare-1.pdf}
\caption{Comparing the same data presented in two map displays. The
choropleth map display in (a)}
\end{figure}

@@

The results will be analysed using a generalised linear model, with a
subject random effect to account for differences in individuals. There
will be two main effects: map type and trend model, which gives the
fixed effects part of the model to be

@@

where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
\(\delta_j\) is the trend model effect. We are allowing for an
interaction between map type and trend model. As the response for
whether the participant detected the data plot is binary, a logistic
model is used.

@@

Figure @ref\{detection\_compare\} display the average detection rates by
type of plot, separately for each trend model. Evaluations on the same
data set are connected by a line segment. For both the Three Cities and
All Cities trend models performance was substantially better for the
hexagon tile map. Viewers detected the data plot substantially more
often with the hexagon tile map. One replicate for the All Cities group,
had similar detection rates for both plot types, and this is discussed
in a later section. Surprisingly, participants could also detect the
gradual spatial trend in the NW-SE group from the hexagon tile map. We
expected that the choropleth map would be superior for the type of
spatial pattern, but the data suggests the hexagon tile map performs
equally as well.

Table \ref{tab:desc_stats} shows the means and standard deviations for
type of plot and each trend model.

@@

\caption{\label{tab:desc_stats}}
\centering
\begin{tabular}[t]{lccc}
\toprule
Type & NW-SE & Three Cities & All Cities\\
\midrule
Choro. & 0.505 & 0.038 & 0.228\\
 & (0.5) & (0.19) & (0.42)\\
Hex. & 0.609 & 0.391 & 0.571\\
 & (0.49) & (0.49) & (0.5)\\
\bottomrule
\end{tabular}
\end{table}

Table XXX is a summary of the mixed effects model. Blah, blah, what we
learn.

@@

The amount of time taken for a participants to submit a response is
explored. The time considered was the amount of time it took for a
participant to submit their choice of plot, the reason for their choice,
and the perceived difficulty of the choice. The time was taken when each
participant hit ``Next''.

The relationship between time taken to submit, and the correct detection
by the participant of the real data display in a lineup is considered in
Figure @ref(fig:hist\_height). The bimodal distributions are similar
across the type of display and the trend model hidden in the real data
plot. The hexagon map displays have a peak for the group that took up to
5 seconds to submit a response. When viewing a choropleth map display,
the second peak occured at around 20 seconds. The longest a participant
took to respond was 60 seconds.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/beeswarm-1.pdf}
\caption{The beeswarm plots show the distribution of the time taken to
submit a response for each combination of trend and type of display. The
time taken shown by the height of the point for each evaluationq1. The
height of the histogram bars show how many evaulations were submitted
within each time window. The orange regions of the bars show the amount
of correct detections, and the green regions are the amount of incorrect
detections.}
\end{figure}

The proportion of correct and incorrect responsesis shown by the width
used to distribute the points horizontally. Each point is randomly
placed, but regions with more points require points to be placed further
from center. For the NW-SE distribution, it is equally likely that quick
responders will be correct or incorrect. It is more likely that
participants picked the correct response if they took longer to respond.
For the Choropelth

However, these quick responders were likely to be either correct or
incorrect. The quick responders viewing a choropleth display were
unlikely to choose correctly, unless viewing a NW-SE trend model.

The choropleth map displays that included a distribution of three cities
was very difficult for participants.

@@

The choices made by participants are examined in Figure
@ref(fig:choices). Participants were misled by the choropleth display,
but not the hexagon display for all cities displays except (2). The maps
with a North West to South East trend was chosen with much greater
frequency in all displays. All of three cities displays, except (4),
were detected in the hexagon display. All except one lineup had at least
one participant select the correct map in the lineup as shown in Figure
@ref(fig:choices).

@@

\begin{figure}
\centering
\includegraphics{figures/aus_cities_3_geo.png}
\caption{``The lineup of choropleth map displays shows a distribution
that affects all capital cities. The values for the inner city areas in
the capital cities result in them being coloured red. However, the
colour blue dominates the display as the large rural areas are filled.
Replicate (2) for all cities.''}
\end{figure}

@@

\hypertarget{modeling-the-difference}{%
\subsection{Modeling the difference}\label{modeling-the-difference}}

The likelihood of detecting the data plot in the lineup can be modelled
using a generalized linear mixed effects model. The base R (R Core Team
\protect\hyperlink{ref-RCore}{2019}) \texttt{glm()} function implements
generalised linear models. The model used includes the two main effects
map type and trend model, which gives the fixed effects model to be:

\hypertarget{detection-rates}{%
\subsubsection{Detection Rates}\label{detection-rates}}

\begin{tabular}{rcrrr}
\toprule
Term & Estimate & Error & Stat & p.value\\
\midrule
Intercept & 0.02 & 0.15 & 0.15 & 0.88\\
Hex & 0.42$^{*  }$ & 0.21 & 1.99 & 0.05\\
Three cities & -3.25$^{***}$ & 0.41 & -7.88 & 0.00\\
All cities & -1.24$^{***}$ & 0.23 & -5.41 & 0.00\\
Hex : Three cities & 2.37$^{***}$ & 0.46 & 5.10 & 0.00\\
\addlinespace
Hex : All cities & 1.08$^{***}$ & 0.31 & 3.47 & 0.00\\
\bottomrule
\end{tabular}

\begin{verbatim}
##                 
##                  Detected? No Detected? Yes
##   Predicted: No           431           121
##   Predicted: Yes          242           310
\end{verbatim}

This gives the model:

\[\widehat{y_{ij}} = 0.0217 + 0.42Hex -3.25_{three} -1.24_{all} + 2.37{Hex.three} + 1.08{Hex.all} \]

\includegraphics{paper_files/figure-latex/glm2-1.pdf}

\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
10, 2020 - 11:55:55

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & detect \\ 
\hline \\[-1.8ex] 
 typeHex. & 0.103$^{**}$ \\ 
  & (0.045) \\ 
  & \\ 
 trendThree Cities & $-$0.467$^{***}$ \\ 
  & (0.045) \\ 
  & \\ 
 trendAll Cities & $-$0.277$^{***}$ \\ 
  & (0.045) \\ 
  & \\ 
 typeHex.:trendThree Cities & 0.250$^{***}$ \\ 
  & (0.063) \\ 
  & \\ 
 typeHex.:trendAll Cities & 0.239$^{***}$ \\ 
  & (0.063) \\ 
  & \\ 
 Constant & 0.505$^{***}$ \\ 
  & (0.034) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 1,104 \\ 
Log Likelihood & $-$675.359 \\ 
Akaike Inf. Crit. & 1,366.719 \\ 
Bayesian Inf. Crit. & 1,406.772 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

For a base model of Choropleth map, using a NW-SE trend model. The
detection rate for Hexagon tile maps using a NW-SE trend model changes
the log odds of the detection by 0.42.

\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
10, 2020 - 11:55:55

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & detect \\ 
\hline \\[-1.8ex] 
 Constant & 0.669$^{***}$ \\ 
  & (0.050) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 1,104 \\ 
Log Likelihood & $-$684.772 \\ 
Akaike Inf. Crit. & 1,379.544 \\ 
Bayesian Inf. Crit. & 1,404.578 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

\% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard
University. E-mail: hlavac at fas.harvard.edu \% Date and time: Fri, Jan
10, 2020 - 11:55:55

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

@@

The demonstrative images of the \texttt{shinydashboard} web application
display the demographic and consent page in Figure @ref(fig:survey1).

@@

\hypertarget{subject-specific-anomolies-0-detection}{%
\subsection{Subject specific anomolies (0\%
detection)}\label{subject-specific-anomolies-0-detection}}

@@

\hypertarget{bibliography}{%
\section{Bibliography}\label{bibliography}}

>>>>

\hypersetup{
            pdftitle={Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics},
            pdfkeywords={statistics, visual inference, geospatial, population},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile
Map for Communicating Cancer Statistics}

@@

Australia is an extreme case of heterogenous geographic units, with
large difference between the smallest and largest geographic units
across various granularities. To communicate information regarding the
small inner-city geographic units of Australian cities an alternative
display must be employed. This will emphasise the value of the statistic
for areas with high population. Figure \ref{fig:liver} shows the
distribution of the smoothed average amount of Liver cancer diagnoses
for Australian Males from 2005-2014. These inner-city areas are not
visible on the choropleth map (a). The hexagon tile map (b) shows orange
hexagons for the inner-city SA2s with higher than average levels of
diagnoses in the capital cities of Melbourne and Sydney. The northern
Queensland, and Northern Territory SA2's with higher than average rates
are still visible but use less map space on the hexagon tile map. There
are still many light blue areas in both displays.

@@

The null model imposed suggests that neighbours are related. The
randomness imposed was smoothed to mirror the practice taken by the
Australian Cancer Atlas. This smoothing allowed neighbours to be related
to each other and show distributions similar to the Liver cancer
distribution shown in \ref{fig:liver}.

@@

Replicate 3 of the All Cities distribution is shown in
\ref{fig:compare}. The same data set is shown in both displays, the
difference is the land area of each SA3 is coloured in the choropleth
and the hexagon representing the SA3 is coloured in the Hexagon Tile
Map. Many maps in the Choropleth lineup (a) are coloured yellow, two are
half light blue, and two are obviously blue. Only one of the maps looks
red.

@@

The likelihood of detecting the data plot in the lineup can be modelled
using a linear mixed effects model. The base R (R Core Team
\protect\hyperlink{ref-RCore}{2019}) \texttt{glm()} function implements
generalised linear models. The model used includes the two main effects
map type and trend model, which gives the fixed effects model to be:

The results will be analysed using a linear mixed effects model, with a
subject random effect to account for differences in individuals. There
will be two main effects: map type and trend model, with an interaction
between them, which gives the fixed effects part of the model to be:

@@

where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the map type effect,
\(\delta_j\) is the trend model effect. We are allowing for an
interaction between map type and trend model. As the response for
whether the participant detected the data plot is binary, a logistic
link model is used.

@@

Figure \ref{fig:detection_compare} displays the average detection rates
by type of plot, separately for each trend model. Evaluations on the
same data set are connected by a line segment. For both the Three Cities
and All Cities trend models performance was substantially better for the
hexagon tile map. Viewers detected the data plot substantially more
often with the hexagon tile map. One replicate for the All Cities group,
had similar detection rates for both plot types, and this is discussed
in the supplementary \protect\hyperlink{lineups}{Lineups} section.
Surprisingly, participants could also detect the gradual spatial trend
in the NW-SE group from the hexagon tile map. We expected that the
choropleth map would be superior for the type of spatial pattern, but
the data suggests the hexagon tile map performs slightly better, or
equally as well.

Table \ref{tab:desc_stats} shows the means and standard deviations of
the detection rate for each type of plot and each trend model. This also
gives the standard errors, the smallest standard deviation is the Three
Cities trend model shown in a Choropleth display. This group had a very
small detection rate of 0.038.

@@

\caption{\label{tab:desc_stats}}
\centering
\begin{tabular}[t]{lccc}
\toprule
Type & NW-SE & Three Cities & All Cities\\
\midrule
Choro. & 0.505 & 0.038 & 0.228\\
 & (0.501) & (0.192) & (0.421)\\
Hex. & 0.609 & 0.391 & 0.571\\
 & (0.489) & (0.489) & (0.496)\\
\bottomrule
\end{tabular}
\end{table}

Table \ref{detect_glm1} is a summary of the generalised linear mixed
effects model, testing the effect of plot type and trend model on
detection rate. The results support the summary from Figure
@ref\{detection\_compare\}. All terms are statistically significant.
Overall, the hexagon tile map performs marginally better than the
choropleth for all trend models, which is a pleasant surprise. Detection
rate is lower for the Three Cities and All Cities, than the NW-SE group.
The hexagon tile map has a substantially higher detection rate than the
choropleth for Three Cities and All Cities. XXX Put a number for each of
these.

\begin{tabular}{rcrr}
\toprule
Term & Estimate & Std. Error & P value\\
\midrule
Intercept & 0.02 & 0.17 & 0.896\\
Hex. & 0.46$^{*  }$ & 0.22 & 0.037\\
Three Cities & -3.43$^{***}$ & 0.42 & 0.000\\
All Cities & -1.35$^{***}$ & 0.24 & 0.000\\
Hex:Three Cities & 2.46$^{***}$ & 0.47 & 0.000\\
\addlinespace
Hex:All Cities & 1.17$^{***}$ & 0.33 & 0.000\\
\bottomrule
\end{tabular}

@@

Figure \ref{fig:beeswarm} shows the time taken for participants to
evaluate each lineup, separately for trend model, whether the data plot
was detected or not, and type of plot, as horizontally jittered dot
plots. The time taken to complete an evaluation ranged from milliseconds
to 60 seconds. The average time taken for type of display is displayed
as a large colored dot on each plot. There is little difference in the
average time taken to read a choropleth or hexgon tile map. There is
also very little difference in evaluation time whether the data plot was
detected or not.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/beeswarm-1.pdf}
\caption{The distribution of the time taken (seconds) to submit a
response for each combination of trend, whether the data plot was
detected, and type of display, shown using horizontally jittered
dotplots. The coloured point indicates average time taken for each plot
type. Although some participants take just a few seconds per evaluation,
and some take as much as mcuh as 60 seconds, but there is very little
difference in time taken between plot types.}
\end{figure}

@@

The choices made by participants are examined in Figure
\ref{fig:choices}. Participants were misled by the choropleth display,
but not the hexagon display for All Cities displays except (2). The maps
with a North West to South East trend was chosen with much greater
frequency in all displays. All of Three Cities displays, except (4),
were detected in the hexagon display. All except one lineup had at least
one participant select the correct map in the lineup as shown in Figure
\ref{fig:choices}.

@@

@@

@@

@@

The demonstrative images of the \texttt{shinydashboard} web application
display the demographic and consent page in Figure \ref{fig:survey1}.

\hypertarget{lineups}{%
\subsection{Lineups}\label{lineups}}

Lineups were created using the Australian Statistical Areas at Level 3.

\begin{figure}
\centering
\includegraphics{figures/aus_cities_3_geo.png}
\caption{The lineup of choropleth map displays hides a distribution that
affects all capital cities.}
\end{figure}

\begin{figure}
\centering
\includegraphics{figures/aus_cities_3_hex.png}
\caption{The lineup of choropleth map displays shows a distribution that
affects all capital cities. The values for the inner city areas in the
capital cities result in them being coloured red. However, the colour
blue dominates the display as the large rural areas are filled.
Replicate (2) for All Cities.}
\end{figure}

The values for the inner city areas in the capital cities result in them
being coloured red. However, the colour blue dominates the display as
the large rural areas are filled. There were no other choropleth maps
that were coloured as blue as map (3). This meant the detection rate was
quite high, participants were able to select the correct distribution
without being able to see the values of the capital cities. The same
data showed in the hexagon tile map display shows varied distributions
across the lineup. They are more diverse in colour than the choropleth
counterparts. The same location holds the real data plot, the red city
centres are now visible and surrounded by yellow, and then blue
hexagons.

@@

@@
